Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Table for res

>>>>

\begin{table}

\begin{tabular}{| r | c | l | r | r |}
\hline
\# & Benchmark  & $\mathcal{F}_{\langle I_c,F_c \rangle}$ & time for approach 1  & time for approach 2 \\\hline
1 & Ball Maglev & & & \\
2 & Cruise Control & & & \\
3 & DC Motor& & & \\
4 & Helicopter & & & \\
5 & Inverted Pendulum 1& & & \\
6 & Inverted Pendulum 2& & & \\
7 & Magnetic Pointer& & & \\
8 & Magnetic Suspension& & & \\
9 & Pendulum& & & \\
10 & Suspension& & & \\
11 & Tape Driver & & & \\
12 & Uscgtamper & & & \\
13 & Satellite & & & \\\hline

\end{tabular}
\caption{Experimental results}
\end{table}
